\textbf{ \Large{Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-06 Paper/PaperJahrSchlich.tex

\todo{citation BILD!}
\begin{figure}[htb]
    \centering
    \includegraphics[scale=0.5]{figures/eDemoboard.png}
    \caption{Layout of the Sun SPOT sensor board}
    \label{fig:SPOT}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \fbox{\includegraphics{figures/missing.jpeg}}
    \caption{class diagram describing the structure of the implemented SHM system}
    \label{fig:UML}
\end{figure}

@@

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure.
The test structure is a 4-story shear-frame consisting of four steel plates with an area of 25\,cm\,$\times$\,50\,cm and a thickness of 0.8\,mm.
Those plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom, the rods are fixed into a solid block of wood with an area of 40\,cm\,$\times$\,60\,cm and a height of 30\,cm.
The SHM system is installed on the test structure by fastening wireless sensor nodes to each story.
The laboratory setup is shown in \autoref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}

@@

The structure is excited by deflecting and releasing the top of the structure.
This excitation method ensures a free vibration in natural frequency with little interferences.
After excitation, the sensor nodes automatically start the acceleration with a sampling rate of 40\,Hz.
To minimize the wireless data communication, each node performs a fast Fourier transform algorithm once sufficient acceleration measurements have been collected.
%Generally FFTs are used to convert equidistant samples of a function into a combination of frequencies, and the corresponding magnitudes, that has the same sample values. 
The acceleration measurements are converted into the vibration frequencies and the corresponding magnitudes of the building.
Each sensor node transfers only the values of the predominating frequency---i.e. the frequency with the biggest magnitude--- \colorbox{cyan}{to the basestation}. The values are then stored in the MySQL database at the host computer.

@@

This paper presents a decentralized autonomous sensor fault detection strategy for structural health monitoring systems using neural networks. 
Autonomous sensor fault detection has been realized by implementing a neural network into each sensor node.
The neural networks have been trained to predict expected sensor measurements to be compared to actual measurments, in oreder to detect sensor faults.
The SHM system has been verified with laboratory experiments, proving that sensor fault detection using neural networks can, improve the dependability and the accuracy of structural health monitoring systems.

>>>>

\todo{citation BILD!}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.5]{figures/eDemoboard.png}
    \caption{Layout of the Sun SPOT sensor board}
    \label{fig:SPOT}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics{figures/uml.pdf}
    \caption{class diagram describing the structure of the implemented SHM system}
    \label{fig:UML}
\end{figure}

@@

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure.
The test structure is a 4-story shear-frame consisting of four steel plates of 25\,cm\,$\times$\,50\,cm and a thickness of 0.8\,mm.
The plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom, the rods are fixed into a solid block of 40\,cm\,$\times$\,60\,cm and a height of 30\,cm.
The SHM system is installed on the test structure by fastening a wireless sensor node to each story.
The laboratory setup after system installation is shown in \autoref{fig:teststructure}.

\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}

@@

This excitation method ensures a free vibration in natural frequency with little interferences.
After excitation, the sensor nodes automatically start the acceleration with a sampling rate of 40\,Hz.
To minimize the wireless data communication, each node performs a fast Fourier transform algorithm once sufficient acceleration measurements have been collected.
%Generally FFTs are used to convert equidistant samples of a function into a combination of frequencies, and the corresponding magnitudes, that has the same sample values. 
The acceleration measurements are converted into the vibration frequencies and the corresponding magnitudes of the building.
Each sensor node transfers only the values of the predominating frequency---i.e. the frequency with the biggest magnitude--- \colorbox{cyan}{to the basestation}. The values are then stored in the MySQL database at the host computer.

@@

This paper has shown a decentralized autonomous sensor fault detection strategy for structural health monitoring systems based on neural networks. 
Autonomous sensor fault detection has been realized by implementing a neural network into each sensor node.
The neural networks have been trained to predict expected sensor measurements to be compared to actual measurments, in order to detect sensor faults.
The SHM system has been verified with laboratory experiments, proving that sensor fault detection using neural networks can improve the dependability and the accuracy of structural health monitoring systems.
